SPARQL on the Open, Decentralised Web

### 2016-11-16 dissertation/introduction.tex
small change #27

We have found that in few cases, at least when evaluating SPARQL
Engines, the evaluation has had a basis in sound statistics or in
philosophy of science and therefore the validity of the conclusions
drawn from them should be challenged. We contributed a new direction
to the statistical problem in Section~\ref{sec:scdoe} and a
philosophical discussion in Section~\ref{sec:scphil}.

>>>>

We have found that in few cases, at least when evaluating SPARQL
Engines, the evaluation has had a basis in sound statistics or in
philosophy of science and therefore the validity of the conclusions
drawn from them should be challenged. We summarise contributions to a
new direction to the statistical problem in Section~\ref{sec:scdoe}
and a philosophical discussion in Section~\ref{sec:scphil}.
